---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
h2 {
  color: #3366cc;
  font-weight: bold;
}

p {
  font-size: 16px;
  line-height: 1.5;
}

body {
  background-color: #fafafa;
}
```

## Dynamic Analysis of YouTube Ad Types and Duration
This dynamic report is based on YouTube push ad data I've recorded over the past week.

Each time I see an ad, I record the ad type, duration, and whether it's the first time I've seen it that day.

Charts and statistics automatically update as the data I enter into my Google Sheet is updated.

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQxuPzFbkPQDA4Negn34-vi7Dt8JUo1pF6g6yp3k1WgnTYirtu8ACsjzcljyJgtuISSvGiIsdwmtz8o/pub?output=csv")

latest_data <- logged_data |>
  rename(
    timestamp = `时间戳记`,
    ad_type = `What type of advertisement did you just see?`,
    duration = `How many seconds is the advertisement?`,
    first_time = `Is this the first time you've seen this ad today?`
  )
```

In the ads I recorded, the average duration was **`r round(mean(latest_data$duration), 1)`** seconds,  
while the longest ad reached **`r max(latest_data$duration)`** seconds.

```{r}
ggplot(latest_data, aes(x = ad_type)) +
  geom_bar(fill = "skyblue") +
  labs(
    title = "Distribution of Advertisement Types",
    x = "Advertisement Type",
    y = "Count"
  )
```

```{r}
ggplot(latest_data, aes(x = first_time)) +
  geom_bar(fill = "pink") +
  labs(
    title = "First Time Seeing the Advertisement?",
    x = "First Time?",
    y = "Count"
  )
```